Cosmology from Kaluza--Klein reduction of five-dimensional Lovelock--Cartan Theory

### 2016-09-12 KKosmology.tex
New abstract by Oscar

\hypersetup{%
  pdftitle={Dimensional reduction on $S^1$ of Lanczos--Lovelock and Lovelock--Cartan theories of gravity},
  pdfauthor={Oscar Castillo-Felisola,}{Cristobal Corral,}{Simon del Pino,}{Francisca Ramirez.},
  pdfkeywords={Torsion,} {Generalised Gravity.},
  pdflang={English}
}

@@

\title{Five-Dimensional Kaluza--Klein Cosmology in Lovelock--Cartan Theory}

@@

%% --------- Abstract
\begin{abstract}
 We study the Kaluza--Klein dimensional reduction of the Lovelock--Cartan theory on a $N$-dimensional Riemann--Cartan manifold, where the compact manifold has $S^1$ topology. First, we focus on the dimensional reduction in presence of torsion, to proceed with the Lovelock--Cartan theory in five dimensions. We find cosmological solutions of the Friedman--Robertson--Walker class for the dimensionally reduced theory. In the five-dimensional vacuum, this theory allows a nontrivial torsion in contrast to the Einstein--Cartan theory. After the dimensional reduction is performed, the torsional degrees of freedom induce a nonvanishing energy-momentum tensor in four dimensions, which behaves as a perfect fluid. Cosmological solutions describing accelerated expansion phases as well as contracting solutions are found. The model shows a dynamical compactification of the extra dimension in some regions of the parameter space. 
\end{abstract}

>>>>

\hypersetup{%
  pdftitle={Cosmology from Kaluza--Klein reduction of five-dimensional Lovelock--Cartan theory},
  pdfauthor={Oscar Castillo-Felisola,}{Cristobal Corral,}{Simon del Pino,}{Francisca Ramirez.},
  pdfkeywords={Torsion,} {Cosmology,}{Kaluza--Klein reduction,}{Generalised Gravity.},
  pdflang={English}
}

@@

\title{Cosmology from  Kaluza--Klein reduction of five-dimensional Lovelock--Cartan Theory}

@@

%% --------- Abstract
\begin{abstract}
  We study the Kaluza--Klein dimensional reduction of the Einstein--Gauss--Bonnet theory on a $N$-dimensional Riemann--Cartan manifold, where the compact dimension has $S^1$ topology. We proceed with a detailed reduction of the Lovelock--Cartan theory in five dimensions. We find cosmological solutions of the Friedman--Robertson--Walker class for the effective theory.
  %%In the five-dimensional vacuum, this theory allows a nontrivial torsion in contrast to the Einstein--Cartan theory.
  The torsional degrees of freedom induce a nonvanishing energy-momentum tensor in four dimensions, which behaves as a perfect fluid. We find cosmological solutions describing accelerated expansion phases as well as contracting universes. The model shows a dynamical compactification of the extra dimension in some regions of the parameter space. 
\end{abstract}
